\datedsubsection{ }
	{%
		2024}
	{%
		\textbf{Does Overconfidence Lead to Procrastination?: A Cognitive Reflection Test Experiment}
    } \\
    \textbf{Supervisor:} \href{https://punarjitroyc.weebly.com}{Dr. Punarjit Roychowdhury}
    \begin{itemize}
        \item Tried to build a bridge between overconfidence and procrastination.
        \item Use of Cognitive Reflection Test to identify overconfident people and studied procrastination behaviour among them.
    \end{itemize}
\vspace{-0.4em}
\datedsubsection{ }
	{%
		2024}
	{%
		\textbf{An Environmental Kuznet’s Curve (EKC) Analysis: A Case Study on Ganga and Yamuna }
    } \\
    \textbf{Supervisor:} \href{https://snu.edu.in/faculty/ram-ranjan/}{Dr. Ram Ranjan} | \textbf{Co-author:} Manya Pahwa, Shiv Nadar University, India
    \begin{itemize}
        \item Created Econometric Model to test for EKC in river Ganga and Yamuna.
        \item  Analyses pollution patterns and tried to identify the cause of pollution in these rivers.
    \end{itemize}
\vspace{-0.4em}
\datedsubsection{ }
	{%
		2022 - 2023}
	{%
		\textbf{Economics of Discrimination: Review of Gary Becker’s work and its application on India}
    } \\
    \textbf{\textit{Dissertation, B.Sc. Economics, XIM University}} |
    \textbf{Supervisors:} \href{http://jnu.ac.in/content/bharateedash}{Dr. Bharatee Bhusana Dash} \& \href{https://www.economics.iitb.ac.in/pintu.html}{Dr. Pintu Parui}
    \begin{itemize}
        \item Criticised Becker (1957) Model of Discrimination
        \item Applied Becker (1957) Model of discrimination to Indian context, through the lens of caste.
    \end{itemize}
\vspace{-0.4em}
\datedsubsection{ }
	{%
		2022}
	{%
		\textbf{Gains from Trade: An Intuition behind Why Countries Exchange}
    } \\
    \textbf{Supervisor:} \href{https://sites.google.com/view/anweshabandyopadhyay/home}{Dr. Anwesha Bandyopadhyay}  | \textbf{Co-author:} Sharanya Roy, XIM University, India
    \begin{itemize}
        \item  Extended the Ricardian Model using quantitative macroeconomic models
        \item Constructed a hypothetical economy to explain the same
    \end{itemize}
